An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-03-06 journal/poly-embed.tex
Tinkering on new example and reorganizing the new property section.

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
\proposedadd{However, we should observe that this statement is not an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.}

It is often convenient to work directly with properties and set aside the losses which elicit them.
We begin with the notion of redundancy.
\begin{definition}[Finite property, non-redundant]
	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

@@

\begin{lemma}\label{lem:embed-defs-equiv}
	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

@@

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/original-top-k}
		\label{fig:original-top-k}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
		\label{fig:finite-surrogate-top-k}
	\end{minipage}
	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
	\label{fig:top-k-simplices}
\end{figure}

@@

\jessie{TODO: Add in example Tikz tree from tikz/hierarchical-property.tex}
\begin{figure}
	\centering
		\includegraphics[width=0.8\linewidth]{tikz/example-tree-deeper.pdf}
		\caption{Tree with distribution $\vec p = (0, .2, .1, .4, .3)$. $gamma(\vec p) = 3$.}
\end{figure}

\begin{figure}
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
	\caption{3 node tree whose property we evaluate in next image.}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
	\caption{Property elicited by unweighted 3-node tree.}
\end{minipage}
\end{figure}

In~\cite[Theorem 1]{ramaswamy2015hierarchical}, they show the property $\gamma := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome is greater than or equal to $1/2$.

In this model, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embeddings and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
In particular, our link construction recovers the link function proposed by~\citet{ramaswamy2018consistent} for abstain loss, as well as another simpler link based on the $L_1$ norm.

@@

% \paragraph{Directions.}
One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
%There are several direct open questions involving the dimension of the surrogate loss.
%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
%Another direction is additional lower bound techniques, or further development of our necessary conditions.

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

>>>>

\usepackage{float}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.  See Lemma~\ref{lem:embed-defs-equiv} to see an equivalence between the two definitions of embedding.}

\jessie{New Lemma here}
\begin{lemma}\label{lem:embed-defs-equiv}
	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

Because of this Lemma, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
We begin with the notion of redundancy.
\begin{definition}[Finite property, non-redundant]
	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

@@

@@

\begin{figure}[H]
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/original-top-k}
		\label{fig:original-top-k}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
		\label{fig:finite-surrogate-top-k}
	\end{minipage}
	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
	\label{fig:top-k-simplices}
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
\end{figure}

\begin{figure}
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
	\caption{3 node tree whose property we evaluate in next image.}
	\label{fig:3-node-tree}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
	\caption{Property elicited by unweighted 3-node tree.}
	\label{fig:3-node-tree-prop}
\end{minipage}
\end{figure}

In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al. show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
They additionally note that this property is agnostic to the weight $W$ of the tree.
As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.

@@

\jessie{Some notes on dimension of this surrogate.}
It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is $1$-embeddable by the characterization of \cite[Section~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embeddings and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses (Theorem~\ref{thm:eps-thick-calibrated}).
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.
In particular, our link construction recovers the link function proposed by~\citet{ramaswamy2018consistent} for abstain loss, as well as another simpler link based on the $L_1$ norm.

@@

% \paragraph{Directions.}
\jessie{Getting rid of this given the COLT-20 paper}
\iffalse
One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
\fi

%There are several direct open questions involving the dimension of the surrogate loss.
%It would be interesting and perhaps practically useful to develop further techniques for upper bounds: automatically constructing embeddings in $\reals^d$ and associated polyhedral losses from a given property, with $d$ as small as possible.
%Another direction is additional lower bound techniques, or further development of our necessary conditions.

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
This material is based upon work supported by the National Science Foundation under Grants No.\ 1657598 and No.\ DGE 1650115.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}
